\textbf{ Matching the forecast horizon with the relevant ecological processes }

### 2019-08-07 doc/manuscript.tex
More edits on discussion

The real challenge is determining what is ``near-term'' and what is ``long-term.'' Furthermore,
many of the forecasts we need in ecology may fall in the intermediate time horizons where neither the time-series
START HERE
approach will be
fully sufficient. Our simulation results demonstrate that there are often extended transitional period where neither approach is effective on its own,
but where a weighted combination of time-series and spatial models can produce highly accurate predictions. Unfortunately there is no clear
way to determine how to weight these two approaches for different time horizons. Our combined ``forecasts'' used the performance of
the forecasts on simulated data to select the weights. This approach cannot be used for actual forecasting because it is effectively an empirical
quantification of the observed performance of the forecasts at different time horizons. Determining how to set these
weights a priori could be pursued using both theoretical and empirical approaches. On the theoretical side, it should be possible to explore the influence
of different parameters on how quickly slow processes (represented in spatial data) begin to influence dynamics. The effects of some parameters are intuitive:
in the community turnover example, increasing the fraction of dispersing individuals causes a more rapid shift in species composition and in model weights
(Fig. \ref{fig:dispersal_niche_width}A). Other factors to consider include organism lifespans, niche widths, and the magnitude of directional environmental
change relative to interannual variation. From an empirical perspective, this challenge could be addressed by using synthetic analyses to estimate the
weighting function. By evaluating both time-series and spatial models for large numbers of forecasts across a range of time-horizons it should be possible
to develop rules of thumb for ensembling models encompassing different scales of processes. This requires data sets that can support the evaluation of
long-term forecasts, which could include paleoecological data (e.g.,), long-term historical data sets (e.g., ), and the use of model systems with
short-generation times (e.g., Petchy), With enough case studies, we might be able to infer patterns that could guide applications in new systems.

>>>>

The challenge is determining what is ``near-term'' and what is ``long-term,'' and how to handle the many forecasts we need in ecology which fall in  intermediate time horizons. Our simulations demonstrate extended transitional periods during which neither the time-series or the spatial approach is effective on its own, but a weighted combination of the two can produce highly accurate predictions. Unfortunately, we currently have no way to determine how to weight these two approaches for different time horizons. Our combined models used weights fitted directly to the simulated data, which is impossible to do for actual forecasting when the future is unknown. We need new theory or empirical case studies in order to set these weights \emph{a priori}. Theory could explore the influence of different parameters on on the rate at which slow processes (represented in spatial data) begin to influence dynamics. The effects of some parameters are intuitive: in the community turnover example, increasing the fraction of dispersing individuals causes a more rapid shift in species composition and in model weights (Fig. \ref{fig:dispersal_niche_width}A). Other factors to consider include organism lifespans, niche widths, and the magnitude of directional environmental change relative to historical interannual variation. Empirical research could address this challenge by accumulating enough case studies to infer patterns in the weight functions and guide applications in new systems. Developing  rules of thumb would require testing many forecasts from both time-series and spatial models across a range of time-horizons. It will require data sets that can support the evaluation of long-term forecasts, which could include paleoecological data (e.g.,), long-term historical data sets (e.g., ), and the use of model systems with short-generation times (e.g., Petchy),

START HERE
